---
title: "UNICEF HIV Prevention - DATA 550 Final project"
author: "Victoria Ngo"
date: "`r Sys.Date()`"
output: html_document
---

```{r, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, here-i-am}
here::i_am("ngo_report.Rmd")
```

```{r, reading-in-packages-and-data}
#load outputs
table1 <- here::here ("output/table1.rds")
figure1 <- here::here("output/figure1.png")
```

# Introduction

This data set compiled by UNICEF describes key indicators in global adolescent HIV prevention from 1999-2023. The data was sourced from nationally representative population-based surveys, such as the AIDS Indicator Survey, Demographic and Health Survey, Multiple Indicator Cluster Survey, and others. Each line of data is a percentage of young persons' knowledge on comprehensive HIV prevention, condom use in high-risk sexual behavior, and HIV testing grouped by sex, age, marital status, urbanicity, geographic region, and wealth quintile where available. The percentile data is grouped by country, data source, year, and demographic. More information on the original dataset can be found [**here**](https://data.unicef.org/resources/dataset/hiv-aids-statistical-tables/) on the UNICEF website by downloading the "Key Indicators in adolescent HIV prevention, 2000-2023" file.

This R Markdown report aims to analyze the characteristics of country statistics by sex, age, marital status, urabanicity, and geographic region. Additionally, this report will visualize the distribution of martial status data collection by the South Asia region.

## Table 1. Collected survey characteristics by sex from 1999-2023

```{r, descriptive-table}
readRDS(
  file = here::here(table1)
)
```

**Table 1.** contains descriptive statistics of the survey populations stratified by sex, age, marital status, urbanicity, and geographic region from population surveys spanning 1999-2023. Each data point is not a study participant, but rather when an annual population-based survey collected data on the listed characteristics. The missing data is representative of data lines not containing information related to the characteristic listed or a survey not collecting data on the characteristic that year.

## Figure 1: Marital Status Collection Trends in South Asia (2006 - 2022)

```{r, figure-1}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(here::here(figure1
))
```

**Figure 1.** shows a time trend of marital statuses that were collected in South Asia between 2006 and 2022 in the adolescent HIV prevention population surveys.
